\LARGE \bf Approximately Orchestrated Road Traffic Automata:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-15 papers/itsc_2012/final.tex
intermediate commit for sec V

Section \ref{sec:map} and \ref{sec:simulation} describe map construction from
OSM data and the simulation engine used in the AORTA framework respectively.

@@

\commentpk{I remember you guys mentioning there was a paper for SUMO describing
a similar process, we should ref it ass to why OSM data is not directly suitable}

@@

AORTA uses microscopic simulation, modeling individual drivers as agents.
Time is modeled discretely, meaning an agent accelerates at a fixed rate for
the duration of a ``step'' to achieve a new position and velocity. Space is
continuous, meaning agents occupy a moving interval of a lane, rather than one
fixed tile of the road. Each step lasts the same fixed duration \textit{dt}.
This lets agents reason about how far they will travel for a given choice of
acceleration before being able to choose a different acceleration. Setting
\textit{dt} to the ``reaction time'' of a human driver may be appropriate for
experiments modeling humans.

Each step, the simulation does the following:

@@

Each step (except 2) will be described below, followed by limitations of the
simulator. Section \ref{sec:config} will describe how researchers may easily
modify relevant portions of AORTA.

@@

Every step, a generator creates some number of new agents. If the agent's route
policy needs computation like pathfinding to operate, the generator either
performs it immediately (incurring a delay in simulation if it is running) or,
if possible, sends it to a pool of worker threads to process in the background.
Once an agent's route is ready, the agent waits alongside its starting lane (as
if it is in a driveway or parking lot). When the lane has no agents that could
potentially crash with the new vehicle, the new agent enters the system with
zero initial speed. % Because behaviors must enforce speed limit along a lane
%from the moment an agent enters a road, it is safe for a new agent to enter a
%road if there is no other agent within the worst-case distance (traveling
%distance at the speed limit, plus stopping distance from this speed) preceeding
%the spawn point. To avoid predicting which agents might enter the lane in the
%near future, there is a buffer space at the beginning of the lane where a new
%agent may never spawn. This disqualifies some short lanes from being spawn
%points, but this is not a big limitation in practice. \commentpk{I understand
%your concern about explaining the entire methodology, but the last 2 lines are
%unnecessary and somewhat distracting}

@@

Intersections check for collisions by examining the turn each agent is
performing and verifying that no other agent is simultaneously performing a
conflicting turn. AORTA has a low-granularity model of turn conflict. If two
vehicles at any point along two different turns could ever come into contact,
then the turns are always in conflict, no matter where the agents actually are
along that turn. This is visualized in figure \ref{fig:conflicts}. The
alternative of tiling intersections \cite{JAIR08-dresner} would provide more
granularity, but it adds computational complexity and would be impractical for
many of the complex intersection geometries inferred from OSM.

When a collision occurs, the simulator throws warnings and halts, since this
indicates a bug in some policy. A future alternative could be to mark the region
as impassable and re-route other traffic away from the accident.

@@

\section{EXTENDING AORTA}
\label{sec:config}

@@

\subsection{Routing Strategies}

>>>>

Sections \ref{sec:map} and \ref{sec:simulation} describe map construction from
OSM data and the simulation engine used in the AORTA framework respectively.

@@

\commentpk{I remember you guys mentioning there was a paper for SUMO describing
a similar process, we should ref it as to why OSM data is not directly suitable}

@@

Different elements of the simulator are described as follows:

\subsection{Simulation Dynamics}

AORTA uses microscopic simulation, modeling individual drivers as point agents
following a simple acceleration-based dynamics model \commentpk{need ideas on
framing the last sentence better}.  Time is modeled discretely, and an
agent accelerates at a fixed rate for the duration of a ``step'' to achieve a
new position and velocity. Space is continuous, meaning agents occupy a moving
interval of a lane, rather than one fixed tile of the road. Each time step
lasts for the same fixed duration, and the simulation does the following after
each time step:

% \textit{dt}.
% This lets agents reason about how far they will travel for a given choice of
% acceleration before being able to choose a different acceleration. Setting
% \textit{dt} to the ``reaction time'' of a human driver may be appropriate for
% experiments modeling humans.
% 
% Each step, the simulation does the following:

@@

\commentpk{need to check the ordering of above enumeration}

@@

Every step, a generator creates some number of new agents. If the agent's route
policy needs computation like pathfinding to operate, the generator either
performs it immediately (incurring a delay in simulation if it is running) or,
if possible, sends it to a pool of worker threads to process in the background.
Once an agent's route is ready, the agent waits alongside its starting lane (as
if it is in a driveway or parking lot). When the lane has no agents that could
potentially crash with the new vehicle, the new agent enters the system. % with
%zero initial speed. Because behaviors must enforce speed limit along a lane
%from the moment an agent enters a road, it is safe for a new agent to enter a
%road if there is no other agent within the worst-case distance (traveling
%distance at the speed limit, plus stopping distance from this speed) preceeding
%the spawn point. To avoid predicting which agents might enter the lane in the
%near future, there is a buffer space at the beginning of the lane where a new
%agent may never spawn. This disqualifies some short lanes from being spawn
%points, but this is not a big limitation in practice. \commentpk{I understand
%your concern about explaining the entire methodology, but the last 2 lines are
%unnecessary and somewhat distracting}

@@

Intersections check for collisions by examining the turn each agent is
performing and verifying that no other agent is simultaneously performing a
conflicting turn. AORTA has a low-granularity model of turn conflict. If two
vehicles at any point along two different turns could ever come into contact,
then the turns are always in conflict, no matter where the agents actually are
along that turn. This is visualized in figure \ref{fig:conflicts}. Further work
is required before higher granularity can be introduced through space-time
tiling intersections \cite{JAIR08-dresner}, due to some of the complex
intersection geometries inferred from OSM \commentpk{If there is an image for
one such complex intersection geometry, we can place it next to the current fig
3 using a subfloat}.

% When a collision occurs, the simulator throws warnings and halts, since this
% indicates a bug in some policy. A future alternative could be to mark the region
% as impassable and re-route other traffic away from the accident.

@@

\subsection{Extending AORTA}
\label{sec:config}

@@
